---
title: "Study 1 (Hive): Clean Regression Analysis"
format:
  html:
    toc: true
    toc-depth: 3
    df-print: paged
execute:
  warning: false
  message: false
editor: source
---

This file produces a clean Study 1 analysis aligned with the latest supervision decisions. The main independent variable is the categorical number of asserted misleading body claims. The six DistilRoBERTa emotion dimensions are analysed separately. Title misinformation and payout are reported as robustness analyses. BH-FDR and joint Wald tests are intentionally omitted from this version.

# 0. Setup

```{r}
#| label: setup

library(tidyverse)
library(arrow)
library(fixest)
library(modelsummary)
library(gt)
library(scales)
library(ggcorrplot)
library(broom)
library(forcats)

rm(list = ls())
set.seed(20260101)
options(encoding = "UTF-8")

base_dir <- "C:\\Users\\batuh\\PycharmProjects\\Thesis\\fact_checked_hive_pipeline"

data_path <- file.path(
  base_dir,
  "6. regression",
  "hive_regression_dataset_main.parquet"
)

output_dir <- file.path(base_dir, "6. regression", "clean_regression_output")
pdf_dir <- file.path(output_dir, "pdf_tables")
html_dir <- file.path(output_dir, "html_tables")
fig_png_dir <- file.path(output_dir, "figures_png")
fig_pdf_dir <- file.path(output_dir, "figures_pdf")
dir.create(pdf_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(html_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(fig_png_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(fig_pdf_dir, recursive = TRUE, showWarnings = FALSE)

if (!file.exists(data_path)) {
  stop("Regression dataset not found: ", data_path)
}

# HC1 heteroskedasticity-robust standard errors.
se_main <- "hetero"

emotion_vars <- c(
  "anger", "disgust", "fear", "joy", "sadness", "surprise"
)

emotion_labels <- c(
  anger = "Anger",
  disgust = "Disgust",
  fear = "Fear",
  joy = "Joy",
  sadness = "Sadness",
  surprise = "Surprise"
)

standing_vars <- c(
  "log_pre_rewards",
  "log_pre_curation",
  "log_pre_posts",
  "log_acct_age"
)

standing_labels <- c(
  log_pre_rewards = "Pre-window cumulative author rewards",
  log_pre_curation = "Pre-window cumulative curation rewards",
  log_pre_posts = "Pre-window post count",
  log_acct_age = "Pre-window account age"
)

control_terms <- c(
  "log_len",
  "is_political",
  "log_images",
  "log_links",
  "log_tags",
  "is_weekend"
)

controls <- paste(control_terms, collapse = " + ")
fe_main <- "category + month"
fe_author <- "category + month + author"

thesis_cols <- c(
  "True-side claims only" = "#4E79A7",
  "At least 1 misleading claim" = "#E15759"
)

interaction_cols <- c(
  "1 misleading claim" = "#4E79A7",
  "2 misleading claims" = "#59A14F",
  "3 misleading claims" = "#E15759"
)

theme_thesis <- function(base_size = 11) {
  theme_minimal(base_size = base_size) +
    theme(
      plot.title = element_text(face = "bold"),
      plot.subtitle = element_text(size = rel(0.95)),
      axis.title = element_text(face = "bold"),
      legend.title = element_text(face = "bold"),
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_blank(),
      strip.text = element_text(face = "bold")
    )
}

save_plot_both <- function(plot_object, file_stub, width = 8, height = 5, dpi = 300) {
  ggsave(
    filename = file.path(fig_png_dir, paste0(file_stub, ".png")),
    plot = plot_object,
    width = width,
    height = height,
    dpi = dpi
  )
  ggsave(
    filename = file.path(fig_pdf_dir, paste0(file_stub, ".pdf")),
    plot = plot_object,
    width = width,
    height = height,
    dpi = dpi,
    device = cairo_pdf
  )
}

# Set to FALSE to skip PDF table export entirely. This makes rendering the
# fastest it can be and fully avoids calling webshot2/Chrome, so the
# "... screenshot completed" progress text can never appear. HTML tables are
# still written and the inline tabbed tables still render.
export_table_pdf <- TRUE

# Run an expression while swallowing every side channel: standard output,
# messages, and warnings. webshot2 prints progress text such as
# "file:///... screenshot completed" while producing a PDF. Inside a
# results = "asis" block that text leaks into the document and breaks the gt
# HTML that follows it. Routing every gtsave call through this keeps the
# rendered output clean.
run_silently <- function(expr) {
  tf <- tempfile()
  con <- file(tf, open = "wt")
  sink(con, type = "output")
  sink(con, type = "message")
  on.exit(
    {
      sink(type = "message")
      sink(type = "output")
      close(con)
      unlink(tf)
    },
    add = TRUE
  )
  invisible(suppressMessages(suppressWarnings(force(expr))))
}

save_gt_table <- function(table_object, file_stub) {
  html_path <- file.path(html_dir, paste0(file_stub, ".html"))
  pdf_path <- file.path(pdf_dir, paste0(file_stub, ".pdf"))

  run_silently(gt::gtsave(table_object, html_path))

  if (isTRUE(export_table_pdf)) {
    tryCatch(
      run_silently(
        gt::gtsave(
          table_object,
          pdf_path,
          expand = 10,
          vwidth = 1400
        )
      ),
      error = function(e) {
        message(
          "Could not export PDF ", basename(pdf_path), ". ",
          "Install webshot2 and make sure Chrome/Chromium is available. ",
          "Original error: ", conditionMessage(e)
        )
      }
    )
  }

  invisible(table_object)
}

# PDF export through gt::gtsave requires webshot2 and Chrome/Chromium.
if (!requireNamespace("webshot2", quietly = TRUE)) {
  message(
    "PDF export requires webshot2. Install once with: ",
    "install.packages('webshot2')"
  )
}
```

# 1. Load and prepare the data

```{r}
#| label: prepare-data

raw_data <- read_parquet(data_path) |>
  as_tibble()

required_columns <- c(
  "doc_id", "author",
  "analysis_sample_body", "analysis_sample_title_robustness",
  "misleading_claim_count", "title_misleading",
  "net_votes", "reblogs", "payout",
  "comments", "upvotes", "downvotes", "distinct_voters",
  "log_len", "is_political", "category", "month",
  "n_images", "n_links", "n_tags", "is_weekend",
  emotion_vars,
  standing_vars
)

missing_columns <- setdiff(required_columns, names(raw_data))
if (length(missing_columns) > 0) {
  stop(
    "The regression dataset is missing required columns: ",
    paste(missing_columns, collapse = ", ")
  )
}

z_score <- function(x) {
  x <- as.numeric(x)
  s <- sd(x, na.rm = TRUE)
  if (is.na(s) || s == 0) return(rep(NA_real_, length(x)))
  as.numeric((x - mean(x, na.rm = TRUE)) / s)
}


model_data <- raw_data |>
  filter(analysis_sample_body %in% TRUE) |>
  mutate(
    misleading_claim_count = as.integer(misleading_claim_count),
    misleading_n_f = factor(misleading_claim_count, levels = 0:3),
    any_misleading_claim = as.integer(misleading_claim_count > 0),
    claim_screen_group = factor(
      if_else(
        any_misleading_claim == 1,
        "At least 1 misleading claim",
        "True-side claims only"
      ),
      levels = c("True-side claims only", "At least 1 misleading claim")
    ),
    title_misleading = as.numeric(title_misleading),

    net_votes = as.numeric(net_votes),
    reblogs = as.numeric(reblogs),
    payout = as.numeric(payout),
    comments = as.numeric(comments),
    upvotes = as.numeric(upvotes),
    downvotes = as.numeric(downvotes),
    distinct_voters = as.numeric(distinct_voters),

    log_net_votes = log1p(pmax(net_votes, 0)),
    log_reblogs = log1p(pmax(reblogs, 0)),
    any_reblog = as.integer(reblogs > 0),
    log_payout = log1p(pmax(payout, 0)),
    log_comments = log1p(pmax(comments, 0)),
    log_upvotes = log1p(pmax(upvotes, 0)),
    log_downvotes = log1p(pmax(downvotes, 0)),
    log_distinct_voters = log1p(pmax(distinct_voters, 0)),

    log_len = as.numeric(log_len),
    is_political = as.numeric(is_political),
    log_images = log1p(pmax(as.numeric(n_images), 0)),
    log_links = log1p(pmax(as.numeric(n_links), 0)),
    log_tags = log1p(pmax(as.numeric(n_tags), 0)),
    is_weekend = as.numeric(is_weekend),

    category = factor(na_if(trimws(as.character(category)), "")),
    month = factor(na_if(trimws(as.character(month)), "")),
    month_chr = as.character(month),
    author = factor(na_if(trimws(as.character(author)), "")),

    across(all_of(emotion_vars), ~ as.numeric(.x)),
    across(all_of(emotion_vars), ~ z_score(.x), .names = "{.col}_z"),

    across(any_of(standing_vars), ~ as.numeric(.x))
  )

invalid_counts <- setdiff(unique(na.omit(model_data$misleading_claim_count)), 0:3)
if (length(invalid_counts) > 0) {
  stop(
    "Unexpected misleading_claim_count values: ",
    paste(invalid_counts, collapse = ", ")
  )
}

standing_coverage <- model_data |>
  summarise(
    across(
      all_of(standing_vars),
      ~ sum(!is.na(.x)),
      .names = "nonmissing_{.col}"
    )
  )

if (any(unlist(standing_coverage) != nrow(model_data))) {
  stop(
    "Pre-window author-standing coverage is incomplete in the body-only ",
    "main sample. Rebuild the dataset with build_regression_dataset_final.py."
  )
}

# H1 samples do not depend on emotion availability.
h1_required <- c(
  "misleading_n_f", control_terms,
  "category", "month", "author"
)

h1_votes_data <- model_data |>
  drop_na(all_of(c("log_net_votes", h1_required)))

h1_reblog_data <- model_data |>
  drop_na(all_of(c("any_reblog", h1_required)))

h1_payout_data <- model_data |>
  drop_na(all_of(c("log_payout", h1_required)))

get_h2_data <- function(outcome, emotion) {
  model_data |>
    drop_na(all_of(c(outcome, h1_required, paste0(emotion, "_z"))))
}

get_title_data <- function(outcome) {
  base_data <- switch(
    outcome,
    log_net_votes = h1_votes_data,
    any_reblog = h1_reblog_data,
    log_payout = h1_payout_data,
    stop("Unknown outcome: ", outcome)
  )

  base_data |>
    filter(
      analysis_sample_title_robustness %in% TRUE,
      !is.na(title_misleading)
    )
}

month_levels <- sort(unique(na.omit(model_data$month_chr)))
model_data <- model_data |>
  mutate(month_f = factor(month_chr, levels = month_levels))

# Dominant emotion descriptive helper.
dominant_emotion_fun <- function(df, emotion_columns) {
  mat <- as.matrix(df[, emotion_columns])
  idx <- max.col(mat, ties.method = "first")
  out <- emotion_columns[idx]
  out[apply(mat, 1, function(x) all(is.na(x)))] <- NA_character_
  out
}

model_data$dominant_emotion <- dominant_emotion_fun(
  model_data,
  emotion_vars
)

model_data <- model_data |>
  mutate(
    dominant_emotion = factor(
      dominant_emotion,
      levels = emotion_vars,
      labels = unname(emotion_labels[emotion_vars])
    )
  )
```

## 1.1 Sample audit

```{r}
#| label: sample-audit

audit_table <- tibble(
  Metric = c(
    "Posts in body-only main sample",
    "Posts in title robustness sample",
    "Authors in body-only sample",
    "Posts with negative net votes",
    "Posts with comments available",
    "Posts with upvotes available",
    "Posts with downvotes available",
    "Posts with distinct voters available",
    "Posts with complete pre-window standing"
  ),
  Value = c(
    nrow(model_data),
    sum(model_data$analysis_sample_title_robustness %in% TRUE, na.rm = TRUE),
    n_distinct(model_data$author),
    sum(model_data$net_votes < 0, na.rm = TRUE),
    sum(!is.na(model_data$comments)),
    sum(!is.na(model_data$upvotes)),
    sum(!is.na(model_data$downvotes)),
    sum(!is.na(model_data$distinct_voters)),
    sum(complete.cases(model_data[, standing_vars]))
  )
)

audit_table
```

# 2. Descriptive statistics and figures

These analyses are descriptive. The formal tests of H1 and H2 are the regression models below.

## 2.1 Distribution of posts by misleading-claim count

```{r}
#| label: desc-claim-count
#| fig-width: 7
#| fig-height: 4.5

p_claim_count <- model_data |>
  count(misleading_claim_count) |>
  ggplot(aes(x = factor(misleading_claim_count), y = n, fill = factor(misleading_claim_count))) +
  geom_col(width = 0.7, show.legend = FALSE) +
  geom_text(aes(label = comma(n)), vjust = -0.35, fontface = "bold", size = 3.6) +
  scale_y_continuous(labels = comma, expand = expansion(mult = c(0, 0.08))) +
  scale_fill_brewer(palette = "Blues") +
  labs(
    title = "Posts by misleading body-claim count",
    x = "Number of asserted misleading body claims",
    y = "Number of posts"
  ) +
  theme_thesis(11)

save_plot_both(p_claim_count, "D1_posts_by_claim_count", 7, 4.5)
p_claim_count
```

## 2.2 Candidate dependent variables by misleading-claim category

These descriptives do not classify entire posts as true or misinformation. The four groups refer only to the number of asserted misleading body claims identified among the classified extracted claims. The pairwise Welch tests compare one, two, and three misleading claims separately with the zero-claim reference group, matching the categorical structure of the regressions.

```{r}
#| label: claim-category-helpers

claim_category_means <- function(data, vars, labels) {
  map_dfr(vars, function(v) {
    d <- data |>
      transmute(
        misleading_claim_count,
        value = as.numeric(.data[[v]])
      ) |>
      filter(
        misleading_claim_count %in% 0:3,
        is.finite(value)
      )

    tibble(
      Variable = v,
      Label = unname(labels[[v]]),
      `Mean: 0 claims` = mean(d$value[d$misleading_claim_count == 0]),
      `Mean: 1 claim` = mean(d$value[d$misleading_claim_count == 1]),
      `Mean: 2 claims` = mean(d$value[d$misleading_claim_count == 2]),
      `Mean: 3 claims` = mean(d$value[d$misleading_claim_count == 3]),
      `N: 0 claims` = sum(d$misleading_claim_count == 0),
      `N: 1 claim` = sum(d$misleading_claim_count == 1),
      `N: 2 claims` = sum(d$misleading_claim_count == 2),
      `N: 3 claims` = sum(d$misleading_claim_count == 3)
    )
  })
}

claim_pairwise_ttests <- function(data, vars, labels) {
  map_dfr(vars, function(v) {
    d <- data |>
      transmute(
        misleading_claim_count,
        value = as.numeric(.data[[v]])
      ) |>
      filter(
        misleading_claim_count %in% 0:3,
        is.finite(value)
      )

    reference <- d$value[d$misleading_claim_count == 0]

    map_dfr(1:3, function(claim_level) {
      comparison <- d$value[d$misleading_claim_count == claim_level]

      if (length(reference) < 2 || length(comparison) < 2) {
        return(NULL)
      }

      test <- t.test(comparison, reference)

      tibble(
        Variable = v,
        Label = unname(labels[[v]]),
        Comparison = paste0(claim_level, " vs 0 claims"),
        Difference = mean(comparison) - mean(reference),
        `t statistic` = unname(test$statistic),
        `p-value` = test$p.value,
        `CI low` = test$conf.int[1],
        `CI high` = test$conf.int[2],
        `N: comparison` = length(comparison),
        `N: 0 claims` = length(reference)
      )
    })
  })
}
```

### 2.2.1 All potential dependent variables

```{r}
#| label: tt-outcomes

dv_candidates <- c(
  log_payout = "Payout",
  log_net_votes = "Net votes",
  log_comments = "Comments",
  log_reblogs = "Reblogs (log count)",
  any_reblog = "Any reblog",
  log_downvotes = "Downvotes",
  log_distinct_voters = "Distinct voters",
  log_upvotes = "Upvotes"
)

available_dv <- names(dv_candidates)[
  names(dv_candidates) %in% names(model_data)
]

dv_category_means <- claim_category_means(
  model_data,
  available_dv,
  dv_candidates
)

dv_category_means_gt <- dv_category_means |>
  select(-Variable) |>
  gt() |>
  fmt_number(columns = starts_with("Mean:"), decimals = 3) |>
  fmt_integer(columns = starts_with("N:")) |>
  tab_header(
    title = "Table D1A. Candidate dependent-variable means by misleading-claim category"
  ) |>
  tab_source_note(
    md(
      "Note. Zero claims is not labelled as a true or fully accurate article. It means that none of the classified asserted claims extracted from the post were coded as misleading."
    )
  )

dv_category_means_gt
save_gt_table(
  dv_category_means_gt,
  "Table_D1A_candidate_DV_means_by_claim_category"
)
```

```{r}
#| label: tt-outcomes-pairwise

dv_pairwise_tests <- claim_pairwise_ttests(
  model_data,
  available_dv,
  dv_candidates
)

dv_pairwise_tests_gt <- dv_pairwise_tests |>
  select(-Variable) |>
  gt(groupname_col = "Label") |>
  fmt_number(
    columns = c(Difference, `t statistic`, `p-value`, `CI low`, `CI high`),
    decimals = 3
  ) |>
  fmt_integer(columns = starts_with("N:")) |>
  tab_header(
    title = "Table D1B. Welch t-tests: each misleading-claim category versus zero claims"
  ) |>
  tab_source_note(
    md(
      "Note. Each comparison is estimated separately: one versus zero, two versus zero, and three versus zero misleading asserted body claims. These are descriptive tests; the regression models provide the main inference."
    )
  )

dv_pairwise_tests_gt
save_gt_table(
  dv_pairwise_tests_gt,
  "Table_D1B_candidate_DV_pairwise_t_tests"
)
```

### 2.2.2 Six discrete emotional-language dimensions

```{r}
#| label: tt-emotions

emotion_category_means <- claim_category_means(
  model_data,
  emotion_vars,
  emotion_labels
)

emotion_category_means_gt <- emotion_category_means |>
  select(-Variable) |>
  gt() |>
  fmt_number(columns = starts_with("Mean:"), decimals = 3) |>
  fmt_integer(columns = starts_with("N:")) |>
  tab_header(
    title = "Table D2A. Emotional-language means by misleading-claim category"
  ) |>
  tab_source_note(
    md(
      "Note. The six DistilRoBERTa emotional-language dimensions are shown separately."
    )
  )

emotion_category_means_gt
save_gt_table(
  emotion_category_means_gt,
  "Table_D2A_emotion_means_by_claim_category"
)
```

```{r}
#| label: tt-emotions-pairwise

emotion_pairwise_tests <- claim_pairwise_ttests(
  model_data,
  emotion_vars,
  emotion_labels
)

emotion_pairwise_tests_gt <- emotion_pairwise_tests |>
  select(-Variable) |>
  gt(groupname_col = "Label") |>
  fmt_number(
    columns = c(Difference, `t statistic`, `p-value`, `CI low`, `CI high`),
    decimals = 3
  ) |>
  fmt_integer(columns = starts_with("N:")) |>
  tab_header(
    title = "Table D2B. Emotional-language Welch t-tests versus zero claims"
  ) |>
  tab_source_note(
    md(
      "Note. One-, two-, and three-claim groups are each compared separately with the zero-claim reference group."
    )
  )

emotion_pairwise_tests_gt
save_gt_table(
  emotion_pairwise_tests_gt,
  "Table_D2B_emotion_pairwise_t_tests"
)
```

## 2.3 Correlation matrix

The categorical misleading-claim predictor is intentionally omitted from the Pearson correlation matrix. Treating the values 0, 1, 2, and 3 as a single continuous scale would impose a linear and equal-distance relationship that the regression design does not assume.

```{r}
#| label: table-D-corr
#| fig-width: 13
#| fig-height: 11

corr_candidates <- model_data |>
  transmute(
    Payout          = log_payout,
    `Net votes`     = log_net_votes,
    Upvotes         = log_upvotes,
    `Distinct voters` = log_distinct_voters,
    Comments        = log_comments,
    Reblogs         = log_reblogs,
    `Any reblog`    = any_reblog,
    Downvotes       = log_downvotes,
    Anger           = anger,
    Disgust         = disgust,
    Fear            = fear,
    Joy             = joy,
    Sadness         = sadness,
    Surprise        = surprise,
    Images          = log_images,
    Links           = log_links,
    Tags            = log_tags,
    Weekend         = is_weekend,
    `Post length`   = log_len,
    Political       = is_political
  ) |>
  mutate(across(everything(), as.numeric))

# Remove variables that are completely missing or have no variation.
valid_corr_vars <- names(corr_candidates)[
  map_lgl(
    corr_candidates,
    ~ sum(!is.na(.x)) > 1 &&
      sd(.x, na.rm = TRUE) > 0
  )
]

corr_candidates <- corr_candidates |>
  select(all_of(valid_corr_vars))

M <- cor(
  corr_candidates,
  use = "pairwise.complete.obs"
)

p_corr <- ggcorrplot(
  M,
  type = "lower",                # Avoid repeating the same correlations twice
  show.diag = TRUE,
  lab = TRUE,
  lab_size = 2.7,
  lab_col = "grey20",
  tl.cex = 10,
  tl.srt = 45,
  colors = c("#6BAED6", "white", "#FB6A4A"),
  outline.color = "white",
  legend.title = "r",
  title = "Correlations: candidate outcomes, emotional language, and controls"
) +
  coord_fixed() +
  theme_thesis(10) +
  theme(
    axis.title = element_blank(),
    axis.text.x = element_text(
      angle = 45,
      hjust = 1,
      vjust = 1,
      size = 9
    ),
    axis.text.y = element_text(
      size = 9
    ),
    plot.title = element_text(
      face = "bold",
      size = 15,
      hjust = 0
    ),
    plot.margin = margin(
      t = 12,
      r = 18,
      b = 28,
      l = 18
    ),
    legend.position = "right"
  )

save_plot_both(
  p_corr,
  "D3_correlations_matrix",
  width = 13,
  height = 11
)

p_corr
```

## 2.4 Posts per month by claim-screen group

```{r}
#| label: desc-time
#| fig-width: 8
#| fig-height: 4.5

mon <- model_data |>
  count(month_f, claim_screen_group)

p_month_counts <- ggplot(mon, aes(month_f, n, fill = claim_screen_group)) +
  geom_col(position = position_dodge(width = 0.8), width = 0.7) +
  geom_text(
    aes(label = comma(n)),
    position = position_dodge(width = 0.8),
    vjust = -0.35,
    fontface = "bold",
    size = 3.2
  ) +
  scale_fill_manual(values = thesis_cols, name = NULL) +
  scale_y_continuous(labels = comma, expand = expansion(mult = c(0, 0.1))) +
  labs(
    title = "Posts per month by presence of asserted misleading claims",
    subtitle = "This descriptive grouping does not classify posts as true versus misinformation",
    x = NULL,
    y = "Number of posts"
  ) +
  theme_thesis(11)

save_plot_both(p_month_counts, "D4_posts_by_month_grouped", 8, 4.5)
p_month_counts
```

## 2.5 Average engagement by dominant emotion and claim-screen group

```{r}
#| label: dominant-emotion-engagement
#| fig-width: 10
#| fig-height: 5

dom_emotion_plot_data <- model_data |>
  filter(!is.na(dominant_emotion)) |>
  group_by(dominant_emotion, claim_screen_group) |>
  summarise(
    mean_log_net_votes = mean(log_net_votes, na.rm = TRUE),
    reblog_rate = mean(any_reblog, na.rm = TRUE),
    n = n(),
    .groups = "drop"
  ) |>
  pivot_longer(
    cols = c(mean_log_net_votes, reblog_rate),
    names_to = "metric",
    values_to = "value"
  ) |>
  mutate(
    metric = recode(
      metric,
      mean_log_net_votes = "Average log net votes",
      reblog_rate = "Reblog rate"
    )
  )

p_dom_emotion <- ggplot(
  dom_emotion_plot_data,
  aes(dominant_emotion, value, fill = claim_screen_group)
) +
  geom_col(position = position_dodge(width = 0.8), width = 0.7) +
  facet_wrap(~ metric, scales = "free_y") +
  scale_fill_manual(values = thesis_cols, name = NULL) +
  labs(
    title = "Average engagement by dominant emotion and claim-screen group",
    subtitle = "Groups indicate zero versus at least one asserted misleading body claim; they are not whole-article truth labels",
    x = NULL,
    y = NULL
  ) +
  theme_thesis(11) +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))

save_plot_both(p_dom_emotion, "D5_engagement_by_dominant_emotion_and_claim_group", 10, 5)
p_dom_emotion
```

## 2.6 Additional descriptive figure: outcomes by misleading-claim count

```{r}
#| label: outcomes-by-claim-count
#| fig-width: 10
#| fig-height: 4.5

outcomes_by_claim <- model_data |>
  group_by(misleading_claim_count) |>
  summarise(
    `Average log net votes` = mean(log_net_votes, na.rm = TRUE),
    `Reblog rate` = mean(any_reblog, na.rm = TRUE),
    `Average log payout` = mean(log_payout, na.rm = TRUE),
    .groups = "drop"
  ) |>
  pivot_longer(
    cols = -misleading_claim_count,
    names_to = "metric",
    values_to = "value"
  )

p_outcomes_by_claim <- ggplot(
  outcomes_by_claim,
  aes(factor(misleading_claim_count), value, fill = factor(misleading_claim_count))
) +
  geom_col(show.legend = FALSE, width = 0.7) +
  facet_wrap(~ metric, scales = "free_y") +
  scale_fill_brewer(palette = "Blues") +
  labs(
    title = "Average outcomes by misleading body-claim count",
    x = "Number of asserted misleading body claims",
    y = NULL
  ) +
  theme_thesis(11)

save_plot_both(p_outcomes_by_claim, "D6_outcomes_by_claim_count", 10, 4.5)
p_outcomes_by_claim
```

```{r}
calculate_concentration <- function(data, outcome, outcome_label) {

  author_totals <- data |>
    group_by(author) |>
    summarise(
      value = sum(
        pmax(.data[[outcome]], 0),
        na.rm = TRUE
      ),
      n_posts = n(),
      .groups = "drop"
    ) |>
    arrange(value)

  total_value <- sum(author_totals$value, na.rm = TRUE)
  n_authors <- nrow(author_totals)

  if (n_authors == 0 || total_value <= 0) {
    stop(
      paste0(
        "Gini cannot be calculated for ",
        outcome_label,
        " because there are no positive values."
      )
    )
  }

  gini <- (
    2 * sum(seq_len(n_authors) * author_totals$value) /
      (n_authors * total_value)
  ) -
    (n_authors + 1) / n_authors

  lorenz_data <- author_totals |>
    mutate(
      cumulative_authors = row_number() / n_authors,
      cumulative_value = cumsum(value) / total_value
    ) |>
    add_row(
      author = NA_character_,
      value = 0,
      n_posts = 0,
      cumulative_authors = 0,
      cumulative_value = 0,
      .before = 1
    )

  plot <- ggplot(
    lorenz_data,
    aes(
      x = cumulative_authors,
      y = cumulative_value
    )
  ) +
    geom_abline(
      slope = 1,
      intercept = 0,
      linetype = "dashed",
      colour = "grey60"
    ) +
    geom_line(
      colour = "#B2182B",
      linewidth = 1.1
    ) +
    annotate(
      "text",
      x = 0.04,
      y = 0.92,
      hjust = 0,
      label = sprintf("Gini = %.2f", gini),
      fontface = "bold",
      size = 4.2
    ) +
    scale_x_continuous(
      labels = scales::percent,
      limits = c(0, 1)
    ) +
    scale_y_continuous(
      labels = scales::percent,
      limits = c(0, 1)
    ) +
    labs(
      title = paste0(
        outcome_label,
        " is concentrated among a small group of authors"
      ),
      subtitle = paste0(
        "Cumulative distribution across authors; ",
        "the dashed line represents perfect equality"
      ),
      x = "Cumulative share of authors",
      y = paste(
        "Cumulative share of",
        tolower(outcome_label)
      )
    ) +
    theme_thesis(11)

  list(
    gini = gini,
    author_totals = author_totals,
    lorenz_data = lorenz_data,
    plot = plot
  )
}
```

```{r}
#| label: author-concentration-plots
#| fig-width: 10
#| fig-height: 6

net_vote_concentration <- calculate_concentration(
  model_data,
  "net_votes",
  "Net votes"
)

payout_concentration <- calculate_concentration(
  model_data,
  "payout",
  "Payout"
)

# Print Gini coefficients
net_vote_concentration$gini
payout_concentration$gini

# Create an output folder
dir.create(
  "figures",
  showWarnings = FALSE,
  recursive = TRUE
)

# Save as high-resolution PNG files
ggsave(
  filename = "figures/D8_net_votes_author_concentration.png",
  plot = net_vote_concentration$plot,
  width = 10,
  height = 6,
  dpi = 300,
  bg = "white"
)

ggsave(
  filename = "figures/D9_payout_author_concentration.png",
  plot = payout_concentration$plot,
  width = 10,
  height = 6,
  dpi = 300,
  bg = "white"
)

# Display plots in the document
net_vote_concentration$plot
payout_concentration$plot
```



# 3. Regression and export helpers

```{r}
#| label: helpers

fit_model <- function(outcome, rhs, data, fixed_effects = NULL) {
  formula_text <- paste0(
    outcome,
    " ~ ",
    rhs,
    if (!is.null(fixed_effects)) paste0(" | ", fixed_effects) else ""
  )

  feols(
    fml = as.formula(formula_text),
    data = data,
    vcov = se_main,
    notes = FALSE
  )
}

fit_main_ladder <- function(outcome, focal_terms, data) {
  list(
    "(1) Body only" = fit_model(outcome, focal_terms, data),
    "(2) + controls" = fit_model(outcome, paste(focal_terms, controls, sep = " + "), data),
    "(3) + category/month FE" = fit_model(outcome, paste(focal_terms, controls, sep = " + "), data, fe_main),
    "(4) + author FE" = fit_model(outcome, paste(focal_terms, controls, sep = " + "), data, fe_author)
  )
}

fit_title_ladder <- function(outcome, data) {
  list(
    "(1) Body only" = fit_model(outcome, "misleading_n_f", data),
    "(2) + title" = fit_model(outcome, "misleading_n_f + title_misleading", data),
    "(3) + controls" = fit_model(
      outcome,
      paste("misleading_n_f + title_misleading", controls, sep = " + "),
      data
    ),
    "(4) + category/month FE" = fit_model(
      outcome,
      paste("misleading_n_f + title_misleading", controls, sep = " + "),
      data,
      fe_main
    ),
    "(5) + author FE" = fit_model(
      outcome,
      paste("misleading_n_f + title_misleading", controls, sep = " + "),
      data,
      fe_author
    )
  )
}

control_coef_map <- c(
  "log_len" = "Log post length",
  "is_political" = "Political post",
  "log_images" = "Log number of images",
  "log_links" = "Log number of links",
  "log_tags" = "Log number of tags",
  "is_weekend" = "Weekend post"
)

h1_coef_map <- c(
  "misleading_n_f1" = "1 misleading claim",
  "misleading_n_f2" = "2 misleading claims",
  "misleading_n_f3" = "3 misleading claims",
  control_coef_map
)

title_coef_map <- c(
  "misleading_n_f1" = "1 misleading claim",
  "misleading_n_f2" = "2 misleading claims",
  "misleading_n_f3" = "3 misleading claims",
  "title_misleading" = "Misleading title",
  control_coef_map
)

emotion_coef_map <- function(emotion) {
  emotion_z <- paste0(emotion, "_z")
  emotion_label <- emotion_labels[[emotion]]

  c(
    "misleading_n_f1" = "1 misleading claim",
    "misleading_n_f2" = "2 misleading claims",
    "misleading_n_f3" = "3 misleading claims",
    setNames(paste0(emotion_label, " (z)"), emotion_z),
    setNames(paste0("1 claim x ", emotion_label), paste0("misleading_n_f1:", emotion_z)),
    setNames(paste0("2 claims x ", emotion_label), paste0("misleading_n_f2:", emotion_z)),
    setNames(paste0("3 claims x ", emotion_label), paste0("misleading_n_f3:", emotion_z)),
    control_coef_map
  )
}

specification_rows <- function(model_names, title_model = FALSE) {
  k <- length(model_names)

  if (title_model) {
    post_controls <- c("No", "No", "Yes", "Yes", "Yes")
    category_fe <- c("No", "No", "No", "Yes", "Yes")
    month_fe <- c("No", "No", "No", "Yes", "Yes")
    author_fe <- c("No", "No", "No", "No", "Yes")
  } else {
    post_controls <- c("No", "Yes", "Yes", "Yes")
    category_fe <- c("No", "No", "Yes", "Yes")
    month_fe <- c("No", "No", "Yes", "Yes")
    author_fe <- c("No", "No", "No", "Yes")
  }

  rows <- tibble(term = c("Post controls", "Category fixed effects", "Month fixed effects", "Author fixed effects"))
  for (i in seq_along(model_names)) {
    rows[[model_names[i]]] <- c(post_controls[i], category_fe[i], month_fe[i], author_fe[i])
  }
  rows
}

make_regression_table <- function(models, coef_map, title, note, file_stub, title_model = FALSE) {
  model_names <- names(models)

  table_object <- modelsummary(
    models,
    stars = c("+" = 0.10, "*" = 0.05, "**" = 0.01, "***" = 0.001),
    coef_map = coef_map,
    statistic = "({std.error})",
    fmt = 3,
    gof_map = tribble(
      ~raw, ~clean, ~fmt,
      "nobs", "Num. Obs.", 0,
      "r.squared", "R-squared", 3,
      "r2.within", "Within R-squared", 3
    ),
    add_rows = specification_rows(model_names, title_model),
    output = "gt",
    title = title,
    escape = FALSE
  ) |>
    tab_source_note(source_note = md(note)) |>
    tab_source_note(source_note = md(
      "Notes: + p < 0.10; * p < 0.05; ** p < 0.01; *** p < 0.001. HC1 heteroskedasticity-robust standard errors in parentheses."
    )) |>
    tab_options(
      table.font.size = px(11),
      data_row.padding = px(3),
      heading.title.font.size = px(15),
      heading.title.font.weight = "bold",
      column_labels.font.weight = "bold"
    )

  save_gt_table(table_object, file_stub)
  table_object
}
```

# 4. H1: Misleading claims and engagement

The reference category is zero misleading body claims among posts with at least one classified asserted body claim.

## 4.1 Net votes

```{r}
#| label: h1-net-votes

h1_votes_models <- fit_main_ladder("log_net_votes", "misleading_n_f", h1_votes_data)

make_regression_table(
  h1_votes_models,
  h1_coef_map,
  "Table 1A. Misleading claims and net votes",
  paste0(
    "The dependent variable is log(1 + max(net votes, 0)). Post controls are log post length, political-post status, log images, log links, log tags, and weekend posting. Individual category, month, and author coefficients are absorbed and are therefore reported as fixed-effect indicators rather than printed separately."
  ),
  "Table_1A_H1_net_votes"
)
```

## 4.2 Reblog probability

```{r}
#| label: h1-reblogs

h1_reblog_models <- fit_main_ladder("any_reblog", "misleading_n_f", h1_reblog_data)

make_regression_table(
  h1_reblog_models,
  h1_coef_map,
  "Table 1B. Misleading claims and reblog probability",
  paste0(
    "The dependent variable equals one when a post received at least one reblog. The models are linear probability models. Post controls are log post length, political-post status, log images, log links, log tags, and weekend posting."
  ),
  "Table_1B_H1_any_reblog"
)
```

# 5. H2: Discrete-emotion moderation

Each emotion is estimated separately. Every table follows the same four-model ladder used for H1.

```{r}
#| label: estimate-h2

fit_h2_ladder <- function(outcome, emotion) {
  emotion_z <- paste0(emotion, "_z")
  data <- get_h2_data(outcome, emotion)
  fit_main_ladder(outcome, paste0("misleading_n_f * ", emotion_z), data)
}

h2_models <- set_names(
  map(
    emotion_vars,
    function(emotion) {
      list(
        log_net_votes = fit_h2_ladder("log_net_votes", emotion),
        any_reblog = fit_h2_ladder("any_reblog", emotion)
      )
    }
  ),
  emotion_vars
)
```

```{r}
#| label: h2-net-votes-build

# Build and save the tables here, outside the results = "asis" block. Any
# webshot2 progress text produced by save_gt_table stays contained in this
# ordinary chunk instead of leaking into the tabbed output below.
h2_netvotes_tables <- set_names(
  map(
    emotion_vars,
    function(emotion) {
      make_regression_table(
        h2_models[[emotion]]$log_net_votes,
        emotion_coef_map(emotion),
        paste0("Table 2. ", emotion_labels[[emotion]], " moderation: net votes"),
        paste0(
          "The emotion score is standardized. Post controls are shown as coefficients. Category, month, and author fixed effects are reported as specification indicators."
        ),
        paste0("Table_2_", emotion, "_net_votes")
      )
    }
  ),
  emotion_vars
)
```

## 5.1 Net votes {.panel-tabset}

```{r}
#| label: h2-net-votes
#| results: asis

for (emotion in emotion_vars) {
  cat("### ", emotion_labels[[emotion]], "\n\n", sep = "")
  cat(gt::as_raw_html(h2_netvotes_tables[[emotion]]))
  cat("\n\n")
}
```

```{r}
#| label: h2-reblogs-build

# Same pattern as the net-votes tables: build and save outside the asis block.
h2_reblog_tables <- set_names(
  map(
    emotion_vars,
    function(emotion) {
      make_regression_table(
        h2_models[[emotion]]$any_reblog,
        emotion_coef_map(emotion),
        paste0("Table 3. ", emotion_labels[[emotion]], " moderation: reblogs"),
        paste0(
          "The dependent variable equals one when a post received at least one reblog. The emotion score is standardized."
        ),
        paste0("Table_3_", emotion, "_any_reblog")
      )
    }
  ),
  emotion_vars
)
```

## 5.2 Reblog probability {.panel-tabset}

```{r}
#| label: h2-reblogs
#| results: asis

for (emotion in emotion_vars) {
  cat("### ", emotion_labels[[emotion]], "\n\n", sep = "")
  cat(gt::as_raw_html(h2_reblog_tables[[emotion]]))
  cat("\n\n")
}
```

## 5.3 Visual summary of H2 net-vote interactions

```{r}
h2_plot_data <- bind_rows(
  extract_interaction_plot_data(
    "(3) + category/month FE"
  ),
  extract_interaction_plot_data(
    "(4) + author FE"
  )
) |>
  mutate(
    specification = recode(
      specification,
      "(3) + category/month FE" =
        "(3) +Category and month FE",
      "(4) + author FE" =
        "(4) +Author FE"
    ),

    # Explicitly determine the left-to-right panel order.
    specification = factor(
      specification,
      levels = c(
        "(3) +Category and month FE",
        "(4) +Author FE"
      )
    ),

    claim_level = factor(
      claim_level,
      levels = c(
        "1 misleading claim",
        "2 misleading claims",
        "3 misleading claims"
      )
    ),

    emotion = factor(
      emotion,
      levels = unname(
        emotion_labels[emotion_vars]
      )
    )
  )
```

```{r}
#| label: h2-netvotes-plot
#| fig-width: 11
#| fig-height: 5.2

h2_plot_data <- h2_plot_data |>
  mutate(
    point_fill = if_else(
      significant,
      as.character(claim_level),
      "Non-significant"
    )
  )

dodge_position <- position_dodge(
  width = 0.55,
  preserve = "single"
)

p_h2_netvotes <- ggplot(
  h2_plot_data,
  aes(
    x = emotion,
    y = estimate,
    colour = claim_level,
    group = claim_level
  )
) +
  geom_hline(
    yintercept = 0,
    linetype = 2,
    colour = "grey55"
  ) +

  geom_errorbar(
    aes(
      ymin = conf.low,
      ymax = conf.high
    ),
    position = dodge_position,
    width = 0.18,
    linewidth = 0.6
  ) +

  # All points are drawn in one layer so their positions remain aligned.
  geom_point(
    aes(fill = point_fill),
    position = dodge_position,
    shape = 21,
    size = 3.2,
    stroke = 1.1
  ) +

  facet_wrap(
    ~ specification,
    nrow = 1
  ) +

  scale_colour_manual(
    values = interaction_cols,
    name = NULL
  ) +

  scale_fill_manual(
    values = c(
      interaction_cols,
      "Non-significant" = "white"
    ),
    guide = "none"
  ) +

  labs(
    title = "Emotional-language interactions and net votes",
    subtitle = paste0(
      "Filled circles indicate statistically significant interactions; ",
      "hollow circles indicate non-significant interactions"
    ),
    x = NULL,
    y = "Interaction coefficient with 95% CI",
    caption = paste0(
      "Coefficients show how the emotional-language slope changes ",
      "relative to posts containing true-side claims only."
    )
  ) +

  theme_thesis(11) +

  theme(
    axis.text.x = element_text(
      angle = 20,
      hjust = 1
    ),
    legend.position = "bottom",
    plot.caption = element_text(
      hjust = 0,
      colour = "grey35",
      size = 9
    )
  )

save_plot_both(
  p_h2_netvotes,
  "D7_H2_netvotes_interactions",
  width = 11,
  height = 5.2
)

p_h2_netvotes
```


# 6. Title robustness

The same title-valid sample is used in all five columns. Title misinformation is a separate predictor and is not added to the body claim count.

## 6.1 Net votes

```{r}
#| label: title-net-votes

title_votes_models <- fit_title_ladder("log_net_votes", get_title_data("log_net_votes"))

make_regression_table(
  title_votes_models,
  title_coef_map,
  "Table R1A. Title robustness: net votes",
  paste0(
    "Restricted title-valid sample. Reference categories are zero misleading body claims and a non-misleading title."
  ),
  "Table_R1A_title_net_votes",
  title_model = TRUE
)
```

## 6.2 Reblog probability

```{r}
#| label: title-reblogs

title_reblog_models <- fit_title_ladder("any_reblog", get_title_data("any_reblog"))

make_regression_table(
  title_reblog_models,
  title_coef_map,
  "Table R1B. Title robustness: reblog probability",
  paste0(
    "Restricted title-valid sample. Linear probability models. Reference categories are zero misleading body claims and a non-misleading title."
  ),
  "Table_R1B_title_any_reblog",
  title_model = TRUE
)
```

# 7. Payout robustness

Payout is reported as a monetary-reward robustness outcome rather than as a primary dependent variable.

## 7.1 H1 payout robustness

```{r}
#| label: payout-h1

h1_payout_models <- fit_main_ladder("log_payout", "misleading_n_f", h1_payout_data)

make_regression_table(
  h1_payout_models,
  h1_coef_map,
  "Table R2. Misleading claims and payout",
  paste0(
    "The dependent variable is log(1 + payout). Payout is a robustness outcome because it is mechanically downstream of stake-weighted voting."
  ),
  "Table_R2_H1_payout"
)
```

## 7.2 Title and payout

```{r}
#| label: payout-title

title_payout_models <- fit_title_ladder("log_payout", get_title_data("log_payout"))

make_regression_table(
  title_payout_models,
  title_coef_map,
  "Table R3. Title robustness: payout",
  paste0(
    "Restricted title-valid sample. The dependent variable is log(1 + payout)."
  ),
  "Table_R3_title_payout",
  title_model = TRUE
)
```

# 8. Model fit for net votes, including pre-window author standing

```{r}
#| label: standing-r2
#| fig-width: 8.5
#| fig-height: 4.6

standing_sample <- h1_votes_data |>
  drop_na(all_of(standing_vars))

r2_models <- list(
  "(1) Body only" = fit_model("log_net_votes", "misleading_n_f", standing_sample),
  "(2) + controls" = fit_model("log_net_votes", paste("misleading_n_f", controls, sep = " + "), standing_sample),
  "(3) + category/month FE" = fit_model("log_net_votes", paste("misleading_n_f", controls, sep = " + "), standing_sample, fe_main),
  "(4) + pre-window standing" = fit_model(
    "log_net_votes",
    paste("misleading_n_f", controls, paste(standing_vars, collapse = " + "), sep = " + "),
    standing_sample,
    fe_main
  ),
  "(5) + author FE" = fit_model("log_net_votes", paste("misleading_n_f", controls, sep = " + "), standing_sample, fe_author)
)

r2_plot_data <- tibble(
  specification = names(r2_models),
  r_squared = map_dbl(r2_models, ~ unname(fixest::fitstat(.x, "r2")[[1]]))
)

p_r2 <- ggplot(r2_plot_data, aes(x = fct_inorder(specification), y = r_squared, fill = specification)) +
  geom_col(width = 0.72, show.legend = FALSE) +
  geom_text(aes(label = sprintf("%.3f", r_squared)), vjust = -0.35, fontface = "bold", size = 3.4) +
  scale_y_continuous(limits = c(0, max(r2_plot_data$r_squared) * 1.08), labels = number_format(accuracy = 0.01)) +
  scale_fill_brewer(palette = "Blues") +
  labs(
    title = "Model fit for net votes",
    subtitle = "The pre-window standing model adds cumulative author rewards, cumulative curation rewards, post count, and account age measured before 01-09-2024",
    x = NULL,
    y = "R-squared"
  ) +
  theme_thesis(11) +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))

save_plot_both(p_r2, "D8_netvotes_model_fit_with_prewindow_standing", 8.5, 4.6)
p_r2
```


# 9. Saved model objects

```{r}
#| label: save-models

all_models <- list(
  h1_votes = h1_votes_models,
  h1_reblogs = h1_reblog_models,
  h1_payout = h1_payout_models,
  h2 = h2_models,
  title_votes = title_votes_models,
  title_reblogs = title_reblog_models,
  title_payout = title_payout_models
)

saveRDS(all_models, file.path(output_dir, "hive_clean_regression_models.rds"))

cat("Tables, figures, and model objects saved under:\n", output_dir, "\n")
```
