---
title: "Study 1 (Hive): Does tokenized engagement reward misinformation?"
format:
  html:
    toc: true
    toc-depth: 3
    df-print: paged
    fig-width: 8
    fig-height: 5
editor: visual
---

This script analyses whether less accurate Hive posts attract more engagement and more reward. It is ordered to be read top to bottom: what the data look like, then a visual exploration, then the central question across every engagement measure, then how small the effect can be, then whether the pattern is concentrated in the most blatant falsehoods, then the moderator, and finally what actually drives engagement plus robustness. Models use `feols`, errors are heteroskedasticity-robust (HC1) and not clustered, and topic (`category`) and `month` are absorbed as fixed effects. Engagement is measured as raw counts or values and logged with `log1p`.

Each engagement outcome is treated as a separate construct grounded in prior work, rather than as a single composite. Net votes correspond to the vote-based engagement measure of Delkhosh et al. (2023) and the approval signals in the engagement funnel of Gonzalez-Bailon et al. (2023); reblogs correspond to the reshare-based diffusion measures of Vosoughi et al. (2018) and Ferrara et al. (2015); comments correspond to the discussion signal counted by Gonzalez-Bailon et al. (2023). Payout and downvotes have no direct empirical precedent in that source set and are included on the basis of the platform's reward and curation design (Hive Blockchain, 2020; Larimer et al., 2016); the closest measured relative of payout is the stake-weighted reward shares used by Delkhosh et al. (2023).

Changelog versus the previous version: outcome labels now name the engagement construct each measure stands for; a documented construct-to-source mapping was added (Section 4); three presentation figures were added (an equivalence plot in Section 7, an emotions-on-reward coefficient plot in Section 10, and a saved topic-effects plot); all presentation figures share one palette and theme and are written to a `figures/` folder; the data path and figure folder are set once at the top. The estimation logic is unchanged.

# 0. Setup

```{r}
#| message: false
#| warning: false
library(tidyverse)   # data handling + plots
library(readxl)      # read the .xlsx dataset
library(janitor)     # clean column names
library(fixest)      # regressions with fixed effects + clustered SE
library(modelsummary)# regression tables and coefficient plots
library(ggcorrplot)  # correlation heatmap
# NOTE: car is NOT attached on purpose. car::recode() would mask dplyr::recode()
# and break every recode() call below. We call car::vif() fully qualified instead.
library(broom)       # tidy model output for custom plots
library(scales)      # percent axis labels
rm(list = ls()); set.seed(20260101)

# ---- paths and a shared presentation look -----------------------------------
# Set the data location once. Change this line if the file moves.
data_path <- "C:\\Users\\batuh\\PycharmProjects\\Thesis\\fact_checked_hive_pipeline\\6. regression\\hive_regression_dataset.xlsx"
fig_dir   <- "figures"                 # every saved figure/table lands here
dir.create(fig_dir, showWarnings = FALSE)

# one palette and one theme so the deck figures match each other
acc_cols <- c("Accurate" = "#2166AC", "Misinformation" = "#B2182B")
sig_cols <- c("p < .05" = "#B2182B", "n.s." = "grey60")
theme_pres <- function(base = 12) {
  theme_minimal(base_size = base) +
    theme(plot.title = element_text(face = "bold"),
          plot.title.position = "plot",
          plot.subtitle = element_text(color = "grey30"),
          panel.grid.minor = element_blank(),
          legend.position = "top")
}
save_fig <- function(name, w = 7, h = 4.5)
  ggsave(file.path(fig_dir, name), width = w, height = h, dpi = 300, bg = "white")

# ---- standard errors --------------------------------------------------------
# Primary inference uses heteroskedasticity-robust (HC1) standard errors, with no
# clustering, so every post is treated as its own observation. Robust rather than
# plain classical errors are used because the outcomes are skewed, which is
# heteroskedasticity that robust errors handle and classical ones do not. To
# cluster by author instead, change this one line to: se_main <- ~author
se_main <- "hetero"
```

```{r}
data <- read_xlsx(data_path) |> clean_names()
```

# 1. Building the variables

We turn raw columns into model variables: log every engagement outcome (they are skewed), standardise emotional language (coefficient read per standard deviation), and build the accuracy measures: the binary misinformation flag and the five-level scale from `final_label`, folding the title-only Model 1 fallbacks into the coarse false and true levels.

```{r}
num <- function(x) suppressWarnings(readr::parse_number(as.character(x)))
emotions <- c("anger","disgust","fear","joy","neutral","sadness","surprise")
emo6     <- c("anger","disgust","fear","joy","sadness","surprise")
eng_raw  <- c("payout","net_votes","distinct_voters","upvotes","downvotes",
              "comments","reblogs","net_rshares")

data <- data |>
  mutate(
    across(all_of(eng_raw), num),
    log_payout    = log1p(pmax(payout, 0)),       # reward
    log_net_votes = log1p(pmax(net_votes, 0)),    # breadth of approval
    log_comments  = log1p(pmax(comments, 0)),     # discussion
    log_reblogs   = log1p(pmax(reblogs, 0)),      # diffusion (reshares)
    log_downvotes = log1p(pmax(downvotes, 0)),    # pushback
    log_distinct_voters = log1p(pmax(distinct_voters, 0)),  # for redundancy check
    log_upvotes         = log1p(pmax(upvotes, 0)),          # for redundancy check
    log_net_rshares     = log1p(pmax(net_rshares, 0)),      # for redundancy check
    comments_count  = pmax(round(comments), 0),
    reblogs_count   = pmax(round(reblogs), 0),
    downvotes_count = pmax(round(downvotes), 0),

    across(all_of(emotions), num),
    emotional_language = num(emotional_language),
    emo_z = as.numeric(scale(emotional_language)),  # standardised (per SD)

    misinformation        = num(misinformation),        # 1 = misinformation, 0 = accurate
    misinformation_strict = num(misinformation_strict), # only where Model 3 committed
    inaccuracy_severity   = num(inaccuracy_severity),   # 1 (true) .. 5 (pants on fire)

    log_len      = num(log_len),       # post length (dominant control)
    is_political = num(is_political),
    month        = as.factor(month),
    author       = as.character(author),

    reputation_ui     = num(reputation_ui),
    effective_vesting = num(effective_vesting),
    log_hp            = log1p(pmax(effective_vesting, 0)),  # log Hive Power
    post_count        = num(post_count)
  )

# five-level accuracy scale from final_label (Model 1 fallbacks -> false/true)
lvl5 <- c("pants_on_fire","false","mostly_false","mostly_true","true")
to_acc5 <- function(fl) {
  fl <- tolower(trimws(as.character(fl)))
  dplyr::case_when(fl %in% lvl5 ~ fl, fl == "misinformation" ~ "false", TRUE ~ NA_character_)
}
data <- data |>
  mutate(acc5_raw   = to_acc5(final_label),
         accuracy_5 = fct_relevel(factor(acc5_raw, levels = lvl5), "true"))  # ref = true

model_data <- data |>
  filter(analysis_sample == TRUE, !is.na(emo_z), !is.na(log_len)) |>
  mutate(category = fct_infreq(factor(category)))  # most common topic = baseline
```

# 2. What does the sample look like?

Counts first, with the small extreme-accuracy cell called out because it carries a key result later.

```{r}
cat("Analysis sample:", nrow(model_data),
    "| unique authors:", dplyr::n_distinct(model_data$author), "\n")
cat("Accuracy (binary): ")
print(table(Misinformation = model_data$misinformation))
cat("\nFive accuracy levels (note the small pants_on_fire cell):\n")
print(table(model_data$acc5_raw, useNA = "ifany"))
```

The engagement outcomes are highly right-skewed (mean far above median, huge maximum), which is why every outcome is logged.

```{r}
model_data |>
  summarise(across(c(payout, net_votes, comments, reblogs, downvotes),
                   list(mean = ~mean(.x, na.rm = TRUE), median = ~median(.x, na.rm = TRUE),
                        max = ~max(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE)))) |>
  pivot_longer(everything(), names_to = c("outcome", ".value"),
               names_pattern = "(.*)_(mean|median|max|sd)") |>
  mutate(across(where(is.numeric), ~round(.x, 2)))
```

```{r}
#| fig-width: 6.5
#| fig-height: 4
ggplot(model_data, aes(log_payout)) +
  geom_histogram(bins = 40, fill = "#4C72B0", color = "white") +
  labs(title = "Distribution of log payout", x = "log(1 + payout)", y = "Posts") +
  theme_pres()
```

Unadjusted group means, descriptive only. Raw gaps here are confounded by topic, length and author, which is why the models below adjust for them, so this is not a test of the hypothesis.

```{r}
model_data |>
  group_by(Accuracy = ifelse(misinformation == 1, "Misinformation", "Accurate")) |>
  summarise(n = n(),
            across(c(payout, net_votes, comments, reblogs, downvotes),
                   ~round(mean(.x, na.rm = TRUE), 2)), .groups = "drop")
```

# 3. Exploring the data visually

These are descriptive views to build intuition before any model. A caution to keep in mind: they are unadjusted, so a slope or a group gap here can reflect topic, length or author rather than emotion or accuracy itself. They show where to look; the adjusted models remain the actual evidence.

```{r}
acc_lab <- function(x) factor(ifelse(x == 1, "Misinformation", "Accurate"),
                              levels = c("Accurate", "Misinformation"))
# short labels for plot axes; construct names are used in the model tables/figures
out_map <- c(log_payout = "Payout", log_net_votes = "Net votes",
             log_comments = "Comments", log_reblogs = "Reblogs", log_downvotes = "Downvotes")
```

### Engagement against each emotion, by accuracy group

`surprise` is shown here only as an illustration of a reusable tool: the function takes any emotion and any outcome. The systematic descriptive view across all seven emotions is the grid below, and the modelled per-emotion estimates are in Section 10. We cut an emotion into bins and plot mean engagement per bin separately for misinformation and accurate posts, with a one-standard-error band. A rising line means engagement climbs with that emotion; a gap between the two lines means the accuracy groups differ at the same emotion level.

```{r}
#| fig-width: 7
#| fig-height: 4.5
plot_emo_outcome <- function(emo, dv, df = model_data, n_bins = 12) {
  d <- df |>
    mutate(grp = acc_lab(misinformation), bin = ntile(.data[[emo]], n_bins)) |>
    group_by(grp, bin) |>
    summarise(x = mean(.data[[emo]]), y = mean(.data[[dv]]),
              se = sd(.data[[dv]]) / sqrt(n()), n = n(), .groups = "drop")
  ggplot(d, aes(x, y, color = grp, fill = grp)) +
    geom_ribbon(aes(ymin = y - se, ymax = y + se), alpha = 0.15, color = NA) +
    geom_line(linewidth = 1) + geom_point(size = 1.8) +
    scale_color_manual(values = acc_cols, name = NULL) +
    scale_fill_manual(values = acc_cols, name = NULL) +
    labs(title = paste0("Mean ", out_map[dv], " by ", emo, " (binned)"),
         subtitle = "Points are bin means; band is +/- 1 SE",
         x = paste(emo, "score"), y = paste0("mean log(1 + ", out_map[dv], ")")) +
    theme_pres()
}
plot_emo_outcome("surprise", "log_net_votes")  # surprise vs engagement
plot_emo_outcome("surprise", "log_payout")      # surprise vs reward
```

### The whole grid: every emotion against every outcome

The single figure to scan first. Rows are outcomes, columns are emotions, and each panel shows binned-mean engagement for the two accuracy groups. Look for steep slopes (the emotion tracks engagement) and separated lines (the accuracy groups differ).

```{r}
#| fig-width: 11
#| fig-height: 8
grid_df <- model_data |>
  mutate(grp = acc_lab(misinformation)) |>
  pivot_longer(all_of(emo6), names_to = "emotion", values_to = "emo_val") |>
  pivot_longer(all_of(names(out_map)), names_to = "outcome", values_to = "eng") |>
  group_by(emotion, outcome, grp) |>
  mutate(bin = ntile(emo_val, 10)) |>
  group_by(emotion, outcome, grp, bin) |>
  summarise(x = mean(emo_val), y = mean(eng), .groups = "drop") |>
  mutate(outcome = dplyr::recode(outcome, !!!out_map))

ggplot(grid_df, aes(x, y, color = grp)) +
  geom_line(linewidth = 0.7) +
  facet_grid(outcome ~ emotion, scales = "free") +
  scale_color_manual(values = acc_cols, name = NULL) +
  labs(title = "Engagement vs each emotion, by accuracy group (binned means)",
       x = "Emotion score", y = "Mean logged engagement") +
  theme_pres(10)
```

### Are the accuracy groups shifted on each outcome?

Boxplots on the logged scale, the descriptive companion to the models. Heavy overlap between the two boxes is the visual form of the null we find later.

```{r}
#| fig-width: 9
#| fig-height: 4
model_data |>
  mutate(grp = acc_lab(misinformation)) |>
  pivot_longer(all_of(names(out_map)), names_to = "outcome", values_to = "eng") |>
  mutate(outcome = dplyr::recode(outcome, !!!out_map)) |>
  ggplot(aes(grp, eng, fill = grp)) +
  geom_boxplot(outlier.alpha = 0.15, width = 0.6) +
  facet_wrap(~outcome, scales = "free_y", nrow = 1) +
  scale_fill_manual(values = acc_cols, guide = "none") +
  labs(title = "Engagement by accuracy group (logged)", x = NULL, y = "log(1 + outcome)") +
  theme_pres(11)
```

### Do misinformation posts feel different?

Which emotion dominates each post, split by accuracy group. Shows whether misinformation posts carry a different emotional signature.

```{r}
#| fig-width: 7
#| fig-height: 4.5
if ("dominant_emotion" %in% names(model_data)) {
  model_data |>
    mutate(grp = acc_lab(misinformation)) |>
    count(grp, dominant_emotion) |>
    group_by(grp) |> mutate(share = n / sum(n)) |>
    ggplot(aes(reorder(dominant_emotion, share), share, fill = grp)) +
    geom_col(position = "dodge") +
    scale_fill_manual(values = acc_cols, name = NULL) +
    scale_y_continuous(labels = percent) + coord_flip() +
    labs(title = "Dominant emotion composition by accuracy group", x = NULL, y = "Share of posts") +
    theme_pres()
}
```

### The dominant predictor in context: payout vs length

Length drives reward, and the accuracy groups overlap almost entirely, which previews why accuracy adds little once length is controlled.

```{r}
#| fig-width: 7
#| fig-height: 4.5
ggplot(model_data, aes(log_len, log_payout, color = acc_lab(misinformation))) +
  geom_point(alpha = 0.15, size = 0.7) +
  geom_smooth(method = "lm", se = TRUE, linewidth = 1) +
  scale_color_manual(values = acc_cols, name = NULL) +
  labs(title = "Payout rises with length; accuracy groups overlap",
       x = "log(length)", y = "log(1 + payout)") +
  theme_pres()
```

# 4. Which engagement measures are distinct, and which are redundant?

The heatmap shows net votes, distinct voters and upvotes are almost perfectly correlated (one variable), and net_rshares is nearly flat once logged. So the analysis keeps five non-overlapping outcomes: payout, net votes, comments, reblogs and downvotes.

These five are not interchangeable, and each one stands in for an engagement construct used in prior work. Net votes track approval, the vote-based signal that Delkhosh et al. (2023) use to measure engagement on a comparable blockchain platform and that appears as likes and reactions in the engagement funnel of Gonzalez-Bailon et al. (2023). Comments track discussion, also counted as engagement by Gonzalez-Bailon et al. (2023). Reblogs track diffusion, the reshare-based spread measured by Vosoughi et al. (2018) and Ferrara et al. (2015). Payout and downvotes are retained on platform-design grounds rather than on a borrowed metric: payout is the token reward the platform allocates over a seven-day window (Hive Blockchain, 2020; Larimer et al., 2016), and its closest measured relative is the stake-weighted rshares of Delkhosh et al. (2023), while downvotes are the curation-side sanction the design makes available (Hive Blockchain, 2020; Larimer et al., 2016).

```{r}
#| fig-width: 7.5
#| fig-height: 6.5
log_cols <- c("log_payout","log_net_votes","log_distinct_voters","log_upvotes",
              "log_downvotes","log_comments","log_reblogs","log_net_rshares")
ggcorrplot(cor(model_data[, log_cols], use = "pairwise.complete.obs"),
           method = "square", type = "lower", lab = TRUE, lab_size = 2.6,
           colors = c("#6BAED6","white","#FB6A4A"),
           title = "Engagement outcomes (logged) - correlation")
```

```{r}
# construct names travel into every model table and forest plot
outcomes <- c("Payout (reward)"        = "log_payout",
              "Net votes (approval)"   = "log_net_votes",
              "Comments (discussion)"  = "log_comments",
              "Reblogs (diffusion)"    = "log_reblogs",
              "Downvotes (pushback)"   = "log_downvotes")
cmap <- c("misinformation" = "Misinformation",
          "misinformation:emo_z" = "Misinformation x Emotional language",
          "emo_z" = "Emotional language (z)", "log_len" = "log(length)")
gof <- "AIC|BIC|Log.Lik.|^F$|RMSE|Std.Errors|R2 Within|R2 Pseudo"
```

# 5. Does misinformation attract more engagement of any kind?

The central question. We fit the same model to each outcome and line up the misinformation coefficient. In the forest plot, a point right of the dashed zero line means misinformation draws more of that engagement; read whether any interval clears zero and in which direction. Reblogs (diffusion) is the outcome that speaks most directly to the spread of misinformation (Vosoughi et al., 2018).

```{r}
fit_full <- function(dv, acc = "misinformation", df = model_data)
  feols(as.formula(paste0(dv, " ~ ", acc, " * emo_z + log_len | category + month")),
        data = df, vcov = se_main)
mis_mods <- lapply(outcomes, fit_full); names(mis_mods) <- names(outcomes)

modelsummary(mis_mods, stars = TRUE, coef_map = cmap, gof_omit = gof,
             title = "Misinformation across engagement outcomes, robust SE (HC1)")
```

```{r}
#| fig-width: 7.5
#| fig-height: 4
modelplot(mis_mods, coef_map = c("misinformation" = "Misinformation"),
          background = list(geom_vline(xintercept = 0, linetype = "dashed", color = "grey50"))) +
  labs(title = "Does misinformation attract more engagement?",
       subtitle = "Misinformation coefficient by outcome (95% CI, robust SE (HC1))",
       x = "Coefficient on the log engagement outcome", y = NULL) +
  theme_pres()
save_fig("01_misinfo_by_outcome.png", w = 7.5, h = 4)
```

The takeaway to expect: the coefficients sit on the zero line for every outcome, including reblogs (diffusion) and downvotes (pushback), so there is no sign that lower accuracy is rewarded with more engagement. The diffusion result matters most, as it is the most direct test of spread.

# 6. Does misinformation earn more payout? Up close on the reward.

Payout is the outcome the thesis is really about, since it is the token reward. We build it up from a raw comparison (1) to the fully adjusted model (5) to show the misinformation coefficient never appears.

```{r}
f <- function(rhs) as.formula(paste0("log_payout ~ ", rhs))
ladder <- list(
  `(1) raw`           = feols(f("misinformation"), model_data, vcov = se_main),
  `(2) + emotion`     = feols(f("misinformation*emo_z"), model_data, vcov = se_main),
  `(3) + controls`    = feols(f("misinformation*emo_z + is_political + log_len"), model_data, vcov = se_main),
  `(4) + topic FE`    = feols(f("misinformation*emo_z + log_len | category"), model_data, vcov = se_main),
  `(5) + topic+month` = feols(f("misinformation*emo_z + log_len | category + month"), model_data, vcov = se_main))
modelsummary(ladder, stars = TRUE, coef_map = cmap, gof_omit = gof,
             title = "Payout (reward) - built up step by step, robust SE (HC1)")
```

Cross-check with Poisson (PPML), which models the counts directly rather than logging them. The misinformation coefficient stays non-significant.

```{r}
pois <- list(
  comments = fepois(comments_count ~ misinformation*emo_z + log_len | category+month, model_data, vcov = se_main),
  reblogs  = fepois(reblogs_count  ~ misinformation*emo_z + log_len | category+month, model_data, vcov = se_main),
  downvotes= fepois(downvotes_count~ misinformation*emo_z + log_len | category+month, model_data, vcov = se_main))
modelsummary(pois, stars = TRUE, coef_map = cmap, gof_omit = gof,
             title = "Count outcomes via Poisson PPML, robust SE (HC1)")
```

# 7. If there is no effect, how small can we say it is?

A non-significant coefficient only says we did not find an effect. The equivalence test (TOST) asks whether the effect is also small enough to rule out, against bounds written as a percent change in the outcome. If `equivalent` is TRUE at a bound, an average effect larger than that bound is rejected.

```{r}
avg_pay <- feols(log_payout  ~ misinformation + emo_z + log_len | category + month, model_data, vcov = se_main)
avg_reb <- feols(log_reblogs ~ misinformation + emo_z + log_len | category + month, model_data, vcov = se_main)

tost <- function(model, term, delta){
  ct <- as.data.frame(coeftable(model)); b <- ct[term,1]; se <- ct[term,2]
  df <- tryCatch(fixest::degrees_freedom(model, type = "t"),
                 error = function(e) model$nobs - length(coef(model)))
  pl <- pt((b + delta)/se, df, lower.tail = FALSE)   # H0: effect <= -delta
  pu <- pt((b - delta)/se, df, lower.tail = TRUE)     # H0: effect >= +delta
  data.frame(estimate = round(b,3), se = round(se,3),
             bound = paste0("+/-", round(delta,3), " (", round(100*(exp(delta)-1)), "%)"),
             tost_p = round(max(pl,pu),4), equivalent = max(pl,pu) < 0.05)
}
bounds <- c(log(1.05), log(1.10), log(1.20))   # 5%, 10%, 20% change
bind_rows(
  cbind(outcome = "payout",  do.call(rbind, lapply(bounds, \(d) tost(avg_pay, "misinformation", d)))),
  cbind(outcome = "reblogs", do.call(rbind, lapply(bounds, \(d) tost(avg_reb, "misinformation", d))))
)
```

Expected reading: diffusion (reblogs) is equivalent to zero even at the tight 5% bound, so misinformation is not linked to more spread and a difference larger than 5% is ruled out. Payout is equivalent only at 20% because it is the noisiest outcome, so its average effect is indistinguishable from zero and bounded at about 20%; we do not claim the tighter bound.

The figure makes the same point visually: the estimate sits on zero, and the question is how wide the interval is relative to the bounds we would consider substantively meaningful.

```{r}
#| fig-width: 7.5
#| fig-height: 3.2
# pull estimate and 95% CI for the misinformation term from the average-effect models
eq_one <- function(model, label){
  ct <- as.data.frame(coeftable(model)); b <- ct["misinformation",1]; se <- ct["misinformation",2]
  data.frame(outcome = label, b = b, lo = b - 1.96*se, hi = b + 1.96*se)
}
eq_df <- bind_rows(eq_one(avg_reb, "Reblogs (diffusion)"),
                   eq_one(avg_pay, "Payout (reward)"))
b10 <- log(1.10); b20 <- log(1.20)

ggplot(eq_df, aes(b, outcome)) +
  annotate("rect", xmin = -b20, xmax = b20, ymin = -Inf, ymax = Inf, fill = "grey88") +
  annotate("rect", xmin = -b10, xmax = b10, ymin = -Inf, ymax = Inf, fill = "grey75") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey40") +
  geom_errorbarh(aes(xmin = lo, xmax = hi), height = 0.14, color = "#B2182B", linewidth = 0.9) +
  geom_point(size = 2.8, color = "#B2182B") +
  scale_x_continuous(sec.axis = sec_axis(~ (exp(.) - 1) * 100, name = "Approx. % change in outcome")) +
  labs(title = "How large could the misinformation effect be?",
       subtitle = "Estimate with 95% CI against +/-10% (dark band) and +/-20% (light band) equivalence bounds",
       x = "Coefficient (log points)", y = NULL) +
  theme_pres()
save_fig("02_equivalence_misinfo.png", w = 7.5, h = 3.2)
```

# 8. Is it only the most blatant falsehoods that differ?

The binary flag and a single linear coefficient both miss the real shape if the relationship is not gradual. Putting the five accuracy levels in directly (each versus `true`) recovers it: engagement is flat across true, mostly true, mostly false and false, and drops sharply only at the extreme, pants on fire. That level rests on just 61 posts, stated honestly.

```{r}
acc5 <- model_data |> filter(!is.na(accuracy_5))
acc5_rename <- c("accuracy_5pants_on_fire"="Pants on fire","accuracy_5false"="False",
                 "accuracy_5mostly_false"="Mostly false","accuracy_5mostly_true"="Mostly true",
                 "emo_z"="Emotional language (z)","log_len"="log(length)")
acc5_fit <- function(dv) feols(as.formula(paste0(dv," ~ accuracy_5 + emo_z + log_len | category + month")),
                               acc5, vcov = se_main)
modelsummary(list(`Payout (reward)` = acc5_fit("log_payout"),
                  `Net votes (approval)` = acc5_fit("log_net_votes"),
                  `Comments (discussion)` = acc5_fit("log_comments"),
                  `Reblogs (diffusion)` = acc5_fit("log_reblogs"),
                  `Downvotes (pushback)` = acc5_fit("log_downvotes")),
             stars = TRUE, coef_map = acc5_rename, gof_omit = gof,
             title = "Five accuracy levels (ref = true) across outcomes, robust SE (HC1)")
```

```{r}
#| fig-width: 7
#| fig-height: 4
modelplot(acc5_fit("log_payout"),
          coef_map = rev(c("accuracy_5mostly_true"="Mostly true","accuracy_5mostly_false"="Mostly false",
                           "accuracy_5false"="False","accuracy_5pants_on_fire"="Pants on fire")),
          background = list(geom_vline(xintercept = 0, linetype = "dashed", color = "grey50"))) +
  labs(title = "Only the most blatant falsehoods earn less",
       subtitle = "log payout vs 'true' (95% CI, robust SE (HC1)); pants on fire n = 61",
       x = "Coefficient vs 'true'", y = NULL) +
  theme_pres()
save_fig("03_accuracy5_payout.png", w = 7, h = 4)
```

Check it is not driven by which authors post extreme content. Author fixed effects compare an author's own posts across accuracy levels. Identification comes only from authors who post at more than one level, so with 61 extreme posts this is underpowered and reported as a check (single-post authors drop, so n falls).

```{r}
acc5_fe <- feols(log_payout ~ accuracy_5 + emo_z + log_len | author + category + month,
                 acc5, vcov = se_main)
modelsummary(list(`between authors` = acc5_fit("log_payout"),
                  `within author (author FE)` = acc5_fe),
             stars = TRUE, coef_map = acc5_rename, gof_omit = gof,
             title = "Five-level payout: between- vs within-author")
```

For contrast, the single-coefficient magnitude version, mostly non-significant because the effect is concentrated at one end rather than gradual. This is why the categorical model above is the one to report.

```{r}
sev_mods <- lapply(outcomes, function(dv)
  feols(as.formula(paste0(dv," ~ inaccuracy_severity + emo_z + log_len | category + month")),
        data = model_data |> filter(!is.na(inaccuracy_severity)), vcov = se_main))
names(sev_mods) <- names(outcomes)
modelsummary(sev_mods, stars = TRUE,
             coef_map = c("inaccuracy_severity"="Inaccuracy (1=true .. 5=pants on fire)",
                          "emo_z"="Emotional language (z)","log_len"="log(length)"),
             gof_omit = gof, title = "Single magnitude coefficient (misses the nonlinearity)")
```

Same five levels using only posts where Model 3 committed a verdict (dropping the title-only fallbacks), to show the extreme-falsehood penalty rests on full-text evidence.

```{r}
acc5_m3 <- acc5 |> filter(label_source == "model3")
modelsummary(list(`Payout (M3 only)` = feols(log_payout ~ accuracy_5 + emo_z + log_len | category+month, acc5_m3, vcov = se_main),
                  `Net votes (M3 only)` = feols(log_net_votes ~ accuracy_5 + emo_z + log_len | category+month, acc5_m3, vcov = se_main)),
             stars = TRUE, coef_map = acc5_rename, gof_omit = gof,
             title = paste0("Five levels, Model 3-committed only (", nrow(acc5_m3), " posts)"))
```

# 9. Does emotional language strengthen the accuracy-engagement link?

The hypothesis is that emotional language makes low-accuracy content more engaging, captured by the interaction `Misinformation x Emotional language`. We read its sign and significance on reward and diffusion; a positive significant interaction would support it.

```{r}
modelsummary(list(`Payout (reward)` = fit_full("log_payout"),
                  `Reblogs (diffusion)` = fit_full("log_reblogs"),
                  `Net votes (approval)` = fit_full("log_net_votes")),
             stars = TRUE, coef_map = cmap, gof_omit = gof,
             title = "Emotional language as a moderator, robust SE (HC1)")
```

Expected reading: the interaction is small, negative and non-significant, so no evidence emotional language strengthens the link. Emotional language carries a weak positive main effect on its own, noted as a minor association rather than support for moderation.

# 10. What actually predicts engagement here?

If accuracy does not drive engagement, what does? These are exploratory, descriptive, not tests. First, the individual emotions and reward.

```{r}
emo_main <- feols(as.formula(paste0("log_payout ~ misinformation + ", paste(emo6, collapse=" + "),
                  " + log_len | category + month")), model_data, vcov = se_main)
emo_rename <- c("misinformation"="Misinformation","anger"="Anger","disgust"="Disgust","fear"="Fear",
                "joy"="Joy","sadness"="Sadness","surprise"="Surprise","log_len"="log(length)")
modelsummary(list(`log payout` = emo_main), stars = TRUE, coef_map = emo_rename, gof_omit = gof,
             title = "Individual emotions and payout (exploratory)")
```

The same result as a coefficient plot, which is the clearer form for the deck: surprise and sadness sit clearly above zero while anger sits below it, so the emotional signal that tracks reward is specific rather than general.

```{r}
#| fig-width: 7
#| fig-height: 4
emo_m  <- coeftable(emo_main)
emo_df <- data.frame(term = rownames(emo_m), b = emo_m[,1], se = emo_m[,2], p = emo_m[,4]) |>
  filter(term %in% emo6) |>
  mutate(label = dplyr::recode(term, !!!emo_rename),
         lo = b - 1.96*se, hi = b + 1.96*se,
         sig = ifelse(p < 0.05, "p < .05", "n.s."))
ggplot(emo_df, aes(b, reorder(label, b), color = sig)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  geom_errorbarh(aes(xmin = lo, xmax = hi), height = 0.25, linewidth = 0.9) +
  geom_point(size = 2.8) +
  scale_color_manual(values = sig_cols, name = NULL) +
  labs(title = "Which emotions track reward?",
       subtitle = "Per-emotion association with log payout (95% CI, robust SE (HC1))",
       x = "Coefficient on log payout", y = NULL) +
  theme_pres()
save_fig("04_emotions_payout.png", w = 7, h = 4)
```

The same per-emotion check across the three substantive outcomes, so the pattern is not read from reward alone. Each emotion enters the model separately; this is the modelled answer to "what does each emotion do to engagement", in contrast to the descriptive binned views in Section 3.

```{r}
#| fig-width: 10
#| fig-height: 4
emo_rhs <- paste(emo6, collapse = " + ")
emo_models <- list(
  `Payout (reward)`      = emo_main,
  `Net votes (approval)` = feols(as.formula(paste0("log_net_votes ~ misinformation + ", emo_rhs, " + log_len | category + month")), model_data, vcov = se_main),
  `Reblogs (diffusion)`  = feols(as.formula(paste0("log_reblogs ~ misinformation + ",   emo_rhs, " + log_len | category + month")), model_data, vcov = se_main)
)
emo_grid <- dplyr::bind_rows(lapply(names(emo_models), function(nm){
  ct <- coeftable(emo_models[[nm]])
  data.frame(outcome = nm, term = rownames(ct), b = ct[,1], se = ct[,2], p = ct[,4])
})) |>
  filter(term %in% emo6) |>
  mutate(outcome = factor(outcome, levels = names(emo_models)),
         label   = dplyr::recode(term, !!!emo_rename),
         lo = b - 1.96*se, hi = b + 1.96*se,
         sig = ifelse(p < 0.05, "p < .05", "n.s."))
ggplot(emo_grid, aes(b, reorder(label, b), color = sig)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  geom_errorbarh(aes(xmin = lo, xmax = hi), height = 0.25) +
  geom_point(size = 2.4) +
  facet_wrap(~ outcome, scales = "free_x") +
  scale_color_manual(values = sig_cols, name = NULL) +
  labs(title = "Each emotion's association with engagement, by outcome",
       subtitle = "Per-emotion coefficients (95% CI, robust SE (HC1)); exploratory, not a hypothesis test",
       x = "Coefficient on the log outcome", y = NULL) +
  theme_pres()
save_fig("06_emotions_by_outcome.png", w = 10, h = 4)
```

Second, topic effects against the baseline topic, the strongest engagement gradient in the data.

```{r}
#| fig-width: 8
#| fig-height: 7
topic_mod <- feols(log_payout ~ misinformation*emo_z + log_len + factor(category) | month,
                   model_data, vcov = se_main)
topic_tbl <- tidy(topic_mod, conf.int = TRUE) |>
  filter(str_detect(term, "factor\\(category\\)")) |>
  mutate(category = str_remove(term, "factor\\(category\\)"),
         sig = ifelse(p.value < 0.05, "p < .05", "n.s."))
ggplot(topic_tbl, aes(estimate, reorder(category, estimate), color = sig)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  geom_point(size = 2) + geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.3) +
  scale_color_manual(values = sig_cols, name = NULL) +
  labs(title = paste0("Topic effects on log payout (ref = ", levels(model_data$category)[1], ")"),
       x = "Coefficient (95% CI, robust SE (HC1))", y = NULL) +
  theme_pres()
save_fig("05_topic_effects.png", w = 8, h = 7)
```

Third, author standing. Reputation and Hive Power strongly predict payout and lift explained variance sharply, so who posts matters far more than whether the post is accurate. Misinformation stays null both with these controls and within author, meaning even an author's own less-accurate posts do not earn more.

```{r}
m_ctrl  <- feols(log_payout ~ misinformation*emo_z + log_len + reputation_ui + log_hp + post_count |
                   category + month, model_data, vcov = se_main)
m_authfe<- feols(log_payout ~ misinformation*emo_z + log_len | author + category + month,
                 model_data, vcov = se_main)
modelsummary(list(`+ standing controls` = m_ctrl, `author FE` = m_authfe),
             stars = TRUE,
             coef_map = c(cmap, "reputation_ui"="Reputation (UI)", "log_hp"="log(Hive Power)",
                          "post_count"="Post count"),
             gof_omit = gof,
             title = "Author standing as controls vs absorbed by author FE (payout)")
```

# 11. Does the result hold up?

The average payout null is reproduced under the stricter Model 3-only label, the graded severity measure, and a sample excluding crypto and gaming.

```{r}
md_strict <- model_data |> filter(!is.na(misinformation_strict))
md_excl   <- model_data |> filter(!category %in% c("crypto_finance","gaming"))
modelsummary(list(
  `strict label` = feols(log_payout ~ misinformation_strict*emo_z + log_len | category+month, md_strict, vcov = se_main),
  `graded severity` = feols(log_payout ~ inaccuracy_severity*emo_z + log_len | category+month, model_data |> filter(!is.na(inaccuracy_severity)), vcov = se_main),
  `excl crypto/gaming` = feols(log_payout ~ misinformation*emo_z + log_len | category+month, md_excl, vcov = se_main)),
  stars = TRUE,
  coef_map = c("misinformation_strict"="Misinformation (strict)",
               "misinformation_strict:emo_z"="Misinformation (strict) x Emotional language",
               "inaccuracy_severity"="Inaccuracy severity",
               "inaccuracy_severity:emo_z"="Inaccuracy severity x Emotional language",
               cmap),
  gof_omit = gof, title = "Robustness - payout, robust SE (HC1)")
```

Diagnostic: variance inflation factors confirm the predictors are not collinear (values near 1 are fine).

```{r}
car::vif(lm(log_payout ~ misinformation*emo_z + is_political + log_len, data = model_data),
         type = "predictor")
```

# 12. Save key tables

```{r}
modelsummary(mis_mods, stars = TRUE, coef_map = cmap, gof_omit = gof,
             output = file.path(fig_dir, "misinfo_by_outcome.html"),
             title = "Misinformation across engagement outcomes")
modelsummary(list(`Payout (reward)` = acc5_fit("log_payout"),
                  `Net votes (approval)` = acc5_fit("log_net_votes"),
                  `Comments (discussion)` = acc5_fit("log_comments"),
                  `Reblogs (diffusion)` = acc5_fit("log_reblogs"),
                  `Downvotes (pushback)` = acc5_fit("log_downvotes")),
             stars = TRUE, coef_map = acc5_rename, gof_omit = gof,
             output = file.path(fig_dir, "five_levels_by_outcome.html"),
             title = "Five accuracy levels across outcomes")
```

# 13. Additional distributional checks

These checks sit on top of the main analysis and do not replace it; every model above is unchanged. Each one stresses the same misinformation model against a specific distributional concern: the zero floor applied to net votes, the long right tail and zero mass in the outcomes, and the influence of the most extreme posts. If the misinformation coefficients stay near zero across all three, the null is not an artifact of the floor, the distribution, or a handful of viral posts.

### 13a. Gross upvotes as a flooring-free approval measure

Net votes is the only outcome that can be negative, because it nets downvote weight against upvote weight, so it is the only place the floor in `log1p(pmax(., 0))` ever binds. Gross upvotes avoid the floor entirely and also separate approval from pushback with no shared term. The line below reports how many posts are affected, and the table places the upvotes model beside the net-votes model so any difference is visible.

```{r}
cat("Posts with net_votes < 0 (the only place pmax binds):",
    sum(model_data$net_votes < 0, na.rm = TRUE), "of", nrow(model_data), "\n")

approval_compare <- list(
  `Net votes (log1p, floored)` = fit_full("log_net_votes"),
  `Upvotes (log1p, no floor)`  = fit_full("log_upvotes")
)
modelsummary(approval_compare, stars = TRUE, coef_map = cmap, gof_omit = gof,
             title = "Approval measure: net votes vs gross upvotes (misinformation model)")
```

### 13b. Poisson pseudo-ML on the raw outcomes

Poisson pseudo-maximum-likelihood models the raw, non-negative outcomes directly, which handles the zero mass and the long tail without logging and avoids the retransformation bias of log-then-OLS. Approval here uses gross upvotes, because a Poisson outcome must be non-negative and net votes can fall below zero. Coefficients read as proportional (semi-elasticity) effects on the outcome.

```{r}
# non-negative raw versions on a separate frame, so model_data is untouched
ppml_df <- model_data |>
  mutate(payout_nn    = pmax(payout, 0),
         upvotes_nn   = pmax(upvotes, 0),
         comments_nn  = pmax(comments, 0),
         reblogs_nn   = pmax(reblogs, 0),
         downvotes_nn = pmax(downvotes, 0))

ppml_outcomes <- c("Payout (reward)"        = "payout_nn",
                   "Upvotes (approval)"     = "upvotes_nn",
                   "Comments (discussion)"  = "comments_nn",
                   "Reblogs (diffusion)"    = "reblogs_nn",
                   "Downvotes (pushback)"   = "downvotes_nn")
ppml_mods <- lapply(ppml_outcomes, function(y)
  fepois(as.formula(paste0(y, " ~ misinformation*emo_z + log_len | category + month")),
         data = ppml_df, vcov = se_main))
names(ppml_mods) <- names(ppml_outcomes)
modelsummary(ppml_mods, stars = TRUE, coef_map = cmap, gof_omit = gof,
             title = "Poisson pseudo-ML on raw outcomes (semi-elasticities), robust SE (HC1)")
```

### 13c. Winsorized at the 99th percentile

Winsorizing caps each outcome at its 99th percentile before logging, so the most extreme posts cannot drive the estimates. If the misinformation coefficients hold here, the main result does not depend on the tail.

```{r}
winsor <- function(x, p = 0.99) pmin(x, quantile(x, p, na.rm = TRUE))
wdf <- model_data |>
  mutate(log_payout_w    = log1p(winsor(pmax(payout, 0))),
         log_net_votes_w = log1p(winsor(pmax(net_votes, 0))),
         log_comments_w  = log1p(winsor(pmax(comments, 0))),
         log_reblogs_w   = log1p(winsor(pmax(reblogs, 0))),
         log_downvotes_w = log1p(winsor(pmax(downvotes, 0))))

wins_outcomes <- c("Payout (reward)"        = "log_payout_w",
                   "Net votes (approval)"   = "log_net_votes_w",
                   "Comments (discussion)"  = "log_comments_w",
                   "Reblogs (diffusion)"    = "log_reblogs_w",
                   "Downvotes (pushback)"   = "log_downvotes_w")
wins_mods <- lapply(wins_outcomes, function(dv)
  feols(as.formula(paste0(dv, " ~ misinformation*emo_z + log_len | category + month")),
        data = wdf, vcov = se_main))
names(wins_mods) <- names(wins_outcomes)
modelsummary(wins_mods, stars = TRUE, coef_map = cmap, gof_omit = gof,
             title = "Winsorized at the 99th percentile (misinformation model), robust SE (HC1)")
```
